\section{Procedure}
\label{sec:procedure}

\subsection{Synthesis}
\label{sec:synthesis}
Firstly we will explain how the YBCO crystal is synthesized. Although there are different methods,
here we used Y$_2$O$_3$, BaCo$_3$ and CuO as raw materials. From these, $\SI{0.454}{g}$ of
Y$_2$O$_3$, $\SI{1.587}{g}$ BaCo$_3$ and $\SI{0.959}{g}$ CuO have to be mixed in a mortar and shall
be grinded to a fine powder.

The finely crushed powder has to be pressed in a mold to form a pellet which will be heated for at
leats 24 hours at $920^\circ$.

Afterwards the pellet shall be crushed and grinded into a powder similar to the first step. For a
final step is has to pressed into a mold for its final shape and heated at $920^\circ$ for another
24 hours. This time it is important to prevent a temperature shock and instead letting the sample
cool down slowly in the furnace. 

We used the digital control of the furnace to both maintain the
temperature but also control the cooling afterwards.

\subsection{4-probe measurement}
\label{sec:4-probe measurement}
Since normal voltmeters have a high error due to contact resistance. Therefore, we measure the
resitance using 4 probes which circumvent this issue
\cite{Hofmann_2009,https://doi.org/10.1002/j.1538-7305.1958.tb03883.x}. A sketch of a sample with
four probes attached and the wiring is shown in \autoref{fig:4-probe-setup}. For this type of
measurement, four probes have to be attached to the sample in a row. A voltage source creates a
voltage between the outer probes (probe 1 and 4 in \autoref{fig:4-probe-setup}) and the current $A$ is
measured. Between the inner probes (2 and 3 in \autoref{fig:4-probe-setup}) the voltage $V$ is measured.
The resistance can be calculated using Ohm`s law
\begin{equation}
  R = \frac{A}{V}.
\end{equation}
Although when considering the resistance of the whole sample another factor appears which relates to
shape and dimensions of the sample.

To minimize the resistance created by the probes, the surface area when contacting the sample has to be
maximized. This has been accomplished by wrapping each probe once around the sample using
soldering alloys. Special attention has to be given to the solder of different probes not touching each
other.

\begin{figure}
  \centering
  \begin{tikzpicture}
    [roundnode/.style={circle, draw=gray, very thick, minimum size=4mm}]
    \draw[rounded corners,fill=gray] (0, 0) rectangle (4, 1) {};

    \draw[rounded corners,fill=lightgray] (0, 0) rectangle (0.5, 1) {};
    \draw[rounded corners,fill=lightgray] (1, 0) rectangle (1.5, 1) {};
    \draw[rounded corners,fill=lightgray] (2.5, 0) rectangle (3, 1) {};
    \draw[rounded corners,fill=lightgray] (3.5, 0) rectangle (4, 1) {};

    \draw[gray, thick] (0.25,1) -- (0.25,2.5);
    \draw[gray, thick] (3.75,1) -- (3.75,2.5);

    \draw[gray, thick] (2.3,2.5) -- (3.75,2.5);
    \draw[gray, thick] (1,2.5) -- (1.7,2.5);
    \node[roundnode] at (2,2.5) {A};
    \draw[gray, thick] (1,2.4) -- (1,2.6);
    \draw[gray, thick] (0.95,2.3) -- (0.95,2.7);
    \draw[gray, thick] (0.95,2.5) -- (0.25,2.5);

    \draw[gray, thick] (1.25,1) -- (1.25,1.75);
    \draw[gray, thick] (2.75,1) -- (2.75,1.75);

    \draw[gray, thick]  (1.25,1.75) -- (1.7,1.75);
    \draw[gray, thick]  (2.3,1.75) -- (2.75,1.75);
    \node[roundnode] at (2,1.75) {V};

    \node[] at (2,-0.2) {YBCO Sample};

    \node[] at (0.25,0.5) {1};
    \node[] at (1.25,0.5) {2};
    \node[] at (2.75,0.5) {3};
    \node[] at (3.75,0.5) {4};
  \end{tikzpicture}
    \caption{4-probe setup to measure the electrical resistance of a YBCO crystal. While a voltage
      is created and current measured between probe 1 and 4, the voltage is measured between the
    inner probes 2 and 3.}
  \label{fig:4-probe-setup}
\end{figure}

\subsection{Measuring $R(T)$}
\label{sec:Measuring $R(T)$}
The afforementioned sample has to be connected to a given circuit board, by using hot soldering.
This board can be connected to a computer which can measure the electrical resistance by applying
the voltages and measuring the currents as explained before. 

For a successful measurement, the sample has to be cooled down and placed in a vacuum while doing
so. While the cooling is needed to reach the critical point and is achieved using a helium-based
heat pump working similar to an air conditioning unit. The vacuum is needed for a more subtle
reason; at cold temperatures the moisture in the air would condensate on the probes and sample,
which could shorten the circuit and either be a source of error or make measurements impossible.

